---
title: "README"
output: github_document
---

GENEActiv_analysis.R: Script to analyze output binary files from GENEActive wearable devices.

Built in R 3.3.2 (Sincere Pumpkin Patch)
 
Author:
   – Jon Clucas, 2017 <jon.clucas@childmind.org>
  
© 2017, Child Mind Institute, Apache v2.0 License
  
Depends on:
  Package 'GENEAread' v 1.1.1
    Maintainer:
      Joss Langford <Joss at activinsights.co.uk>
    Author:
      – Zhou Fang
  Published: 2013-04-23
  License: GPL-2 | GPL-3
  Documentation:
    https://cran.r-project.org/web/packages/GENEAread/GENEAread.pdf
      
  Package 'GGIR' v 1.4
    Author:
      – Vincent T van Hees <vincentvanhees@gmail.com>
    Contributors:
      – Zhou Fang
      – Jing Hua Zhao
      – Joe Heywood
      – Severine Sabia
    Date/Publication: 2017-01-22 17:02:09
    License: LGPL (≥ 2.0, < 3)
    Documentation:
      https://cran.r-project.org/web/packages/GGIR/GGIR.pdf

```{r setup, include=FALSE}
Encoding("UTF-8")
# our GENEActive data
setwd("/Volumes/Data/Research/ITL/GENEActiv/Data/")
# exclude the partial data CSVs; include only full-data binaries
g_files <- list.files()[endsWith(list.files(), '.bin')]
# subset the recordings captured 2017 Feb 20-22,
# offloaded Feb 22 & Feb 24
g_files <- g_files[grepl('02-22', g_files) | grepl('02-24', g_files)]

# GENEActiv analysis libraries
require(GENEAread)
require(GGIR)

# dependencies
require(mmap)
require(lubridate)
require(ggplot2)
# GENEAread function `read.bin` returns an AccData object
# AccData factors for the device we are testing are:
#   timestamp
#   x
#   y
#   z
#   light
#   button
#   temperature
arno_foot_l <- read.bin(g_files[1])
arno_foot_r <- read.bin(g_files[2])
arno_hand <- read.bin(g_files[3])
curt_hand <- read.bin(g_files[4])
jon_hand <- read.bin(g_files[5])

AccDatas <- c('arno_foot_l', 'arno_foot_r', 'arno_hand', 'curt_hand', 'jon_hand')
processing_times <- c(2.219 * 60, 3.077 * 60, 3.916, 12.753 * 60, 3.57)
pt2 <- c(39.367, 25.765, 3.652, 9.103*60, 3.991)
record_frames <- c(14803200, 10368000, 2009100, 33276000, 1728000)
record_RAM <- c(829, 581, 113, 1863, 97)
fq <- c(85.7, 60, 20, 100, 10)
dur <- c(48, 48, 168, 168, 48)
meta <- data.frame(g_files, AccDatas, fq, dur, processing_times, pt2, record_frames, record_RAM)
remove(AccDatas, processing_times, pt2, record_frames, record_RAM, fq, dur)
```

The relative timecost of processing does appear to decrease with increased recording frequency, although the absolute timecost naturally rises. Here are the processing times of two iterations of processing the same five binary files.

arno_foot_l : 85.7 Hz : 48 hrs :
Processing took: 2.219 mins .
Loaded 14803200 records (Approx  829 MB of RAM)
17-02-20 17:00:00.500 (Mon)  to  17-02-22 16:58:24.488 (Wed) 
Processing took: 39.367 secs .
Loaded 14803200 records (Approx  829 MB of RAM)
17-02-20 17:00:00.500 (Mon)  to  17-02-22 16:58:24.488 (Wed) 

arno_foot_r : 60.0 Hz : 48 hrs:
Processing took: 3.077 mins .
Loaded 10368000 records (Approx  581 MB of RAM)
17-02-20 17:00:00.500 (Mon)  to  17-02-22 17:00:00.483 (Wed) 
Processing took: 25.765 secs .
Loaded 10368000 records (Approx  581 MB of RAM)
17-02-20 17:00:00.500 (Mon)  to  17-02-22 17:00:00.483 (Wed) 

arno_hand : 30.0 Hz : 168 hrs:
Processing took: 3.916 secs .
Loaded 2009100 records (Approx  113 MB of RAM)
17-02-20 17:00:00.500 (Mon)  to  17-02-21 12:31:58.964 (Tue) 
Processing took: 3.652 secs .
Loaded 2009100 records (Approx  113 MB of RAM)
17-02-20 17:00:00.500 (Mon)  to  17-02-21 12:31:58.964 (Tue)

curt_hand : 100.0 Hz : 168 hrs:
Processing took: 12.753 mins .
Loaded 33276000 records (Approx  1863 MB of RAM)
17-02-20 17:00:00.500 (Mon)  to  17-02-24 13:26:00.490 (Fri)
Processing took: 9.103 mins .
Loaded 33276000 records (Approx  1863 MB of RAM)
17-02-20 17:00:00.500 (Mon)  to  17-02-24 13:26:00.490 (Fri) 

jon_hand : 10.0 Hz : 48 hrs:
Processing took: 3.57 secs .
Loaded 1728000 records (Approx  97 MB of RAM)
17-02-20 17:00:00.500 (Mon)  to  17-02-22 17:00:00.400 (Wed) 
Processing took: 3.991 secs .
Loaded 1728000 records (Approx  97 MB of RAM)
17-02-20 17:00:00.500 (Mon)  to  17-02-22 17:00:00.400 (Wed) 

```{r plot processing time}
plot(meta$record_frames, meta$processing_times, xlab = "number of frames captured", ylab = "processing time", main="Processing Time by number of frames captured, 2 trials")
abline(lm(meta$processing_times ~ meta$record_frames))
points(meta$record_frames, meta$pt2, pch = 2, col="#0067a0")
abline(lm(meta$pt2 ~ meta$record_frames), col="#0067a0")
```

```{r gather data, include=FALSE}
# put all of our data from the same time range into a single dataframe
acc_df <- function(df, acc, device, start_time, end_time){
  # function to bind acc data to a dataframe
  # 
  # Parameters
  # ----------
  # df : dataframe
  #   the dataframe we'll be binding to
  # 
  # acc : AccData
  #   the acc data we'll be binding
  #   
  # device : string
  #   the name we wnat in the "device" column for this acc data
  # 
  # start_time : double (lubridate ymd_hms), optional
  #   the start_time at which we cut off recording values
  #   defaults to `ymd_hms("2017-02-20 17:00:00 EST")`
  #   
  # end_time : double (lubridate ymd_hms), optional
  #   the end_time at which we cut off recording values
  #   defaults to `ymd_hms("2017-02-22 17:00:00 EST")`
  # 
  # Returns
  # -------
  # df : dataframe
  #   the original dataframe with the additional acc data appended
  if(missing(start_time)){
    start_time = ymd_hms("2017-02-20 17:00:00 EST")
  }
  if(missing(end_time)){
    end_time = ymd_hms("2017-02-22 17:00:00 EST")
  }
  accdf <- data.frame(ymd_hms(acc$page.timestamps[ymd_hms(
           acc$page.timestamps) <= end_time & ymd_hms(acc$page.timestamps) >= 
           start_time]), acc$x[ymd_hms(acc$page.timestamps) <= end_time & 
           ymd_hms(acc$page.timestamps) >= start_time], acc$y[ymd_hms(
           acc$page.timestamps) <= end_time & ymd_hms(acc$page.timestamps) >= 
           start_time], acc$z[ymd_hms(acc$page.timestamps) <= end_time &
           ymd_hms(acc$page.timestamps) >= start_time], acc$light[ymd_hms(
           acc$page.timestamps) <= end_time & ymd_hms(acc$page.timestamps) >= 
           start_time], acc$button[ymd_hms(acc$page.timestamps) <= end_time & 
           ymd_hms(acc$page.timestamps) >= start_time], acc$temperature[
           ymd_hms(acc$page.timestamps) <= end_time & ymd_hms(
           acc$page.timestamps) >= start_time], c(device))
  return(rbind(df, accdf))
}
# initialize dataframe
acc_data <- data.frame(timestamp=double(), x=double(), y=double(), z=double(), 
            light=double(), button=double(), temperature=double(), device=
            factor())
# append each acc data
acc_data <- acc_df(acc_data, arno_hand, "Arno hand")
acc_data <- acc_df(acc_data, arno_foot_l, "Arno left foot")
acc_data <- acc_df(acc_data, arno_foot_r, "Arno right foot")
acc_data <- acc_df(acc_data, curt_hand, "Curt hand")
acc_data <- acc_df(acc_data, jon_hand, "Jon hand")
names(acc_data) = c('timestamp', 'x', 'y', 'z', 'light', 'button', 'temperature', 'device')
```

```{r plot light over time by device}
ggplot(acc_data, aes(x=timestamp, y=light)) + geom_point(aes(col=factor(
       device), shape=factor(device))) + labs(title = 
       "Light exposure over time by device") + guide_legend(title = "Device")
```


